% Include this at the start of a Chapter Same level as _Main.tex You should then
% be able to make it as a stand alone text file.
% Make sure you add the footer too!!!
\input{_chapterHeader}
\section{Backgrounds}
\subsection{Birthplaces}
This section is about establishing the origin of your character, where they were born and the environment they grew up in. The birthplace you select will influence your character's skills, perks, and potentially their story. Keep in mind that your character's race must match one of the options in the province or country, or you will need to provide an in-game explanation for why your character originates there.
Picking Birthplace
Choose Continent of Birth and gain the Language of that Continent and the Bonus.
Choose the Area that you were born in that's below the continent that you selected and gain the associated language or Skill Ranks, however bear in mind that some areas may not be applicable if your race is not local to the area.
\subsubsection{Non Jadarag}
If you are not playing in the Jadarag setting the GM can give a different variety of Skills. This can be the following:
\begin{itemize}
\item A Language at Skill Rank 6
\item A Racial/Kingdom specific language at Skill Rank 6 or 2 Skill Points.
\item 8 Skill Points: 2 Points for Combat Skill, 1 Point For Non-Combat Skill however if a Read or Write Skill you gain 2 Ranks for the price of 1.
\end{itemize}
\subsubsection{Jadarag}
\subsubsection{Continent of Ardonia}
Ardonia is a vast and culturally diverse continental realm forged from the remnants of ancient empires, divine wars, and shattered alliances. It spans across fertile plains, jagged mountain ranges, highland forests, and war-torn borders, and is home to a web of interconnected governments, each rooted in shared history but divided by geography, ideology, and ambition.
Ardonia is governed by noble houses who operate within semi-autonomous realms, tied together by shared faiths, trade routes, and historical treaties. The people of Ardonia are very professional and proud of their jobs.
\begin{itemize}
\item Language Common 6
\item 4 Professional Skill Points.
\item 1 Professional Skill may start at Rank 7.
\item \MakePerkLink{Minor Contact} in a different Kingdom.
\end{itemize}
\subsubsubsection{Alliance of Daetarre}
The Alliance of Daetarre is a loose but enduring confederation of highland city-states, cliffhold dominions, and forestbound enclaves nestled along the northwestern mountains beyond Mon'ur's borders. Formed centuries ago to repel invasions and preserve autonomy, the Alliance is bound by mutual defence pacts, trade accords, and deep cultural respect for ancestral rites, elemental magic, and martial honour. Though each member-state retains its sovereignty, they convene through the Stone Accord Council, where leaders debate through ritualized challenge or vote. Known for producing elite rangers, sky-climbers, and storm-scribes, the Daetarre Alliance maintains a rugged neutrality, serving as both a buffer and a wildcard in the ongoing tensions between Mon'ur and the Kingdom of Macedon.
\begin{itemize}
\item Any Race
\item Atrayan Skill Rank 6
\item Rank 1: \MakeSkillLink{Athletics}, \MakeSkillLink{Concealment}, \MakeSkillLink{Crafting} - Bowyer , \MakeSkillLink{Guerrilla Tactics}, \MakeSkillLink{Stealth}, \MakeSkillLink{Survival}.
\item Rank 2: \MakeSkillLink{Missile Weapon} - Bow
\end{itemize}
\subsubsubsection{Breakland of Daetarre}
The Breaklands of Daetarre are a fractured archipelago of fiercely independent city-states, spread across a rugged coastal landmass surrounded on all sides by sea. The Breaklands are a mosaic of competing port-cities, merchant republics, cliffhold enclaves, and storm-battered hillforts—each with its own laws, traditions, and ruling councils. What binds them is not a crown, but a shared maritime culture, ancestral reverence, a pact of mutual defence and non-aggression ratified through sea-oaths and seasonal gatherings. The region thrives on trade, seafaring, boasting fleets of windcutters, stormpriests, and salt-born diplomats. While they rarely act as one, the Breaklanders are highly adaptive, fiercely proud, and experts in both coastal warfare and political manoeuvrings. To outsiders, the Breaklands may seem divided—but beneath the shifting sails and rival banners lies a deep unity born of survival, sea, and storm.
\begin{itemize}
\item Any Race
\item Atrayan, Nordheimer, Quinyan at Skill Rank 2
\item \MakeSkillLink{Athletics}, \MakeSkillLink{Missile Weapon} - Bow, \MakeSkillLink{Swimming}, \MakeSkillLink{Sailing}
\item \MakeSkillLink{Lore} - Monsters, \MakeSkillLink{Sailing}
\end{itemize}
\newpage
\subsubsection{Isles of }
\subsubsubsection{Duchy of Calradia}
\subsubsubsection{Kingdom of Andrastes}
\newpage
\subsection{Stages of development}
\subsubsection{Bloodline}
\subsubsection{Upbringing}
\subsubsection{Adolescence}
\subsubsection{Heritage}
\subsubsection{Development Table}
\subsection{Stages of development}
\subsubsection{Arcane Education}
\subsubsection{Bastion of Arms}
\input{_chapterFooter} % See Header