

\begin{longtable}{%
    >{\raggedright\arraybackslash}p{0.3\textwidth} % Left-aligned
    C{0.2\textwidth}                               % Centered
    p{0.5\textwidth}                               % Justified
}
\hline
\textbf{Skill} & \textbf{Recommended Attributes} & \textbf{Description} \\
\hline
\endfirsthead

\hline
\textbf{Skill} & \textbf{Recommended Attributes} & \textbf{Description} \\
\hline
\endhead

\endfoot

\hline
\endlastfoot
Acrobatics & Agility, Perception, Wisdom & This used when attempting to balance, roll, dive, tumble. \\
Acting & Perception, Wisdom, Intelligence & The skill to convince someone that you’re some one else, disguise your self or just outright lie. You may also Distract at GMs discretion using an opposed roll Vs Willpower + Perception that reduces opponents awareness pools. \\
Alchemy & Intelligence & The ability of mixing and making lotions and potions and the value of those items. Toxicology etc \\
Administration & Intelligence & This is the ability to govern a village or logistically manage a large group of people. \\
Appraising & Wisdom, Intelligence & This is a more generic knowledge at trying to work out an items value, normally a survivalist will known the average cost of a trap, this allows you to have general knowledge. \\
Astrology & Wisdom, Intelligence & The study of the movements and relative positions of celestial bodies interpreted as having an influence on human affairs and the natural world. \\
Athletics & Agility, Wisdom, Strength, Constitution, Intelligence & This skill allows you to increase your movement when running, you can jump large gaps and even row a boat, but also gives you the ability to go the ‘distance' and have some knowledge of common injuries in this field. \\
Awareness & Perception & The skill to perceive your surroundings using your senses, distinguish friend from foe and spot hidden enemies. \\
Bargain & Perception, Wisdom & With this your able to negotiate lower prices, and use previous knowledge to that effect as well. You would know that steel in one city seems to differ in another etc. \\
Battle Surgery & Perception, Intelligence & Used to treat the badly wounded with the appropriate equipment when ‘Magic’ isn’t available or doesn’t work or it is to expensive. This is also a more in-depth view of racial anatomy. Can be used for diagnosis. Can treat Major Wound-Expiring Levels. Successes required equal to wound level. Excess successes give 1A/S to Targets Constitution roll and allows them to make an immediate Constitution Roll at TN7. Can only reduce the above wound levels by 1 per week. \\
Beast Riding & Agility, Wisdom & You use this skill in place of an Athletics roll when your mounted on a traditional mount such as a Dire Wolf, Great Eagles, Raptors etc. This also acts as a cap when being used in combat. See MOUNTED COMBAT. \\
Building & Strength, Intelligence, Wisdom & This is not just the skill to lay a brick but to also work out where exactly a building should be built, architecture and surveying of that building or structure as well. \\
Brawling - Unarmed & Agility, Strength & Gives you the basis of fisticuffs, street fighting and grappling with an opponent when you have no weapons but your own hands. \\
Cartography & Perception, Intelligence & This allows you to navigate and make the maps used by Empires, Kingdoms. \\
Climbing & Agility, Strength, Constitution, Perception, Wisdom & This is mountaineering, bouldering, free climbing, the skill to use ropes and pulleys to get yourself and others up and over an obstacle. \\
\hline
\end{longtable}

