\begin{multicols}{2}
\subsection{Drakien}

“So many friends gone, and for what purpose” – Victor Drakor, Grand Master of the Watchers of Reliance

This race was made by dragons, and said to be the mixture of Elves and Dragons who took a human like form. The god known as Reliance has direct descendants that have ruled much of the Isles of Appia since the 1st Devourer war and the Dragon isles for even longer.

Appearance

Drakiens are tall, powerful humanoids who embody a regal fusion of elven grace and draconic heritage. Drakiens possess broad, commanding physiques built for both nobility and war. Their skin ranges in tone from warm human hues to a distinctive copper-toned sheen that catches the light with a faint glow. Upon closer inspection, this skin reveals a fine scale-like texture, most notably along the neck, where overlapping draconic scales subtly rise from the collarbone to the jawline—an elegant yet undeniable marker of their bloodline.

Their facial features are angular and striking, with high cheekbones, defined jawlines, and intense, glowing eyes that range in colours like golden yellow, fiery red, or deep violet—each with vertical, reptilian pupils that betray their ancient ancestry. Drakiens have slightly elongated ears that sweep back close to the skull, a trait that gives them an elven silhouette without fully matching their kin. 

Subtle bone ridges are sometimes present along the cheekbones or brows, and in rare cases, short horn stubs or claw-like protrusions appear on their forearms. Hair is typically dark—ranging from deep brown to black—and worn long, often braided or tied back, especially among warriors and nobles.

Height and Weights

Drakien Male and Female height is very similar between 6’5ft - 7’5ft, unlike many races however their height can continue to grow incredibly slowly with age. average weight of Drakiens is 95-160kg

Life Expectancy

Unknown, no Drakien has died from old age. They are considered out of Adolescence at 20. Drakiens sleep like most races but 6 hours is considered a Full Rest.

Attributes Maximum
\begin{itemize}
\item Strength : 9
\item Agility: 7
\item Constitution: 8
\item Intelligence: 7
\item Wisdom: 6
\item Perception: 6
\item Magic/Faith: 7
\end{itemize}

Racial Attributes
Strength +3, Agility +1, Constitution +2, Intelligence +1, Magic or Faith +1

Attributes Average
Drakien will often have an average of Strength 6, Agility 4, Constitution 5, Intelligence 4, Wisdom and Perception of 3.

Favoured Profession
Drakiens favour the professions of Nobles, Knights, Paladins, Priests or Mages.

Racial Perks
Night Vision, Poison Resistance, Disease Resistance, Dragon Blood.
\begin{itemize}
\item Perk Points: 21
\item Legacy Points: 4
\item Base Movement: 5
\end{itemize}

Gods Worshipped: Reliance, Zenos are mainly worshipped however some Drakien have been known to worship others in rare circumstances.
\end{multicols}