\begin{multicols}{2}
\subsection{Dune Lizards}

“Friends are not plentiful , to much hatred for us since the Devourer Wars” – Amagat Barakis – Mage of Gallamor

The Lizards are warm blooded and they were once as numerous as the Human race but they made an error of picking the wrong side during the Devourer Wars that
resulted in the other races committing mass genocide upon
their race. Only the Dune Lizards remain and since the
Cataclysm they are not hated as they once were but some
of the races with longer lifespans tend to view them with
distrust. They are Proud and Loyal and this tendency has
sometimes led to their undoing.

Appearance 
Dune Lizards are tall, humanoid reptilian beings shaped by the harsh environments of the desert. Their physiques are built for endurance and survival, with dense musculature, thick hide-like scales, and an imposing presence.

Their skin is made of rough, scaled plates in desert-adapted tones—ranging from sun-bleached sand and muted grey to earthen rust and deep slate. Bone protrusions are commonly visible on the head, forehead, or jawline, giving many individuals a naturally armoured look. Their heads are distinctly lizard-like: elongated, with slitted nostrils, sharp eyes, and no visible external ears. Their eyes are typically reptilian—bright, reflective, and well-suited for navigating both searing daylight and moonlit dunes.

Each hand and foot ends in four digits tipped with curved talons, capable of gripping, climbing, and slashing. Their tails, though often partially hidden beneath layered desert wrappings or armour, provide balance and can be used in combat or defence.

Height and Weights
Dune Lizards Male and Female height is very similar between 5’5ft - 6’5ft. Dune Lizard females are slightly broader than males but average weight is 85-140kg.

Life Expectancy
Their lifetime commonly ranges from 70-90 years due to their constitution. Has a normal sleeping pattern like humans.

Attributes Maximum
\begin{itemize}
\item Strength: 6
\item Agility: 6
\item Constitution: 8
\item Intelligence: 6
\item Wisdom: 6
\item Perception: 6
\item Magic/Faith: 6
\end{itemize}


Attribute Points: 4
Racial Attributes: Constitution +2

Attributes Average
Dune Lizards will often have an Average of 3 in each individual attribute except Constitution where it is normally 5, however these can increase by an additional 1 point in a given profession.

Favoured Profession
Dune Lizards can suit a variety of Roles and are not known to stick to one single profession.

Racial Perks

Night Vision, Enhanced Smell, Leathery Skin.
\begin{itemize}
\item Perk Points: 35
\item Legacy Points: 3
\item Base Movement: 4
\end{itemize}

Gods Worshipped: All
\end{multicols}